---
title: "analysis"
output: html_document
date: "2023-04-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
rm(list=ls())

# all models only have one difference in parameter 
freedom <- 1 
```


# TAS1R1 
## Log Likelihood Values (F1x4)
TAS1R1 (Human Foreground): -10799.382943 (parameters = 45)
TAS1R1 (Null): -10800.166623 (parameters: 44)
TAS1R1 (Homo-Pan Foreground): -10800.166524 (parameters = 45)

```{r}
# null likelihood 
f1x4_null_likelihood <- -10800.166623 

#####################################################################################################################
# HUMAN FOREGROUND 
# input log-likelihood values 
f1x4_hum_alt_likelihood <- -10799.382943
f1x4_hum_statistic <- 2 * (f1x4_hum_alt_likelihood - f1x4_null_likelihood)
p_value <- 1 - pchisq(f1x4_hum_statistic, freedom) # calculate p-value

# create data frame with results
resultsdf <- data.frame(name = "f1x4_hum_alt_TAS1R1", likelihood_ratio_test = f1x4_hum_statistic , p_value = p_value)

#####################################################################################################################
# HOMININI FOREGROUND 
# input log-likelihood values 
f1x4_pan_alt_likelihood <- -10800.166524
f1x4_pan_statistic <- 2 * (f1x4_pan_alt_likelihood - f1x4_null_likelihood)
p_value2 <- 1 - pchisq(f1x4_pan_statistic, freedom) # calculate p-value

# create data frame with results
resultsdf2 <- data.frame(name = "f1x4_pan_alt_TAS1R1", likelihood_ratio_test = f1x4_pan_statistic, p_value = p_value2)
resultsdf <- rbind(resultsdf, resultsdf2)

```

## Log Likelihood Values (Fmutsel)
TAS1R1 (Human Foreground): -10463.428637 (parameters = 48)
TAS1R1 (Null): -10464.152917 (parameters = 47)
TAS1R1 (Homo-Pan Foreground): -10464.152130 (parameters = 48)

```{r}
# null likelihood 
fmutsel_null_likelihood <- -10464.152917 

#####################################################################################################################
# HUMAN FOREGROUND 
# input log-likelihood values 
fmutsel_hum_alt_likelihood <- -10463.428637
fmutsel_hum_statistic <- 2 * (fmutsel_hum_alt_likelihood - fmutsel_null_likelihood)
p_value3 <- 1 - pchisq(fmutsel_hum_statistic, freedom) # calculate p-value

# create data frame with results
resultsdf3 <- data.frame(name = "fmutsel_hum_alt_TAS1R1", likelihood_ratio_test = fmutsel_hum_statistic, p_value = p_value3)
resultsdf <- rbind(resultsdf, resultsdf3)

#####################################################################################################################
# HOMININI FOREGROUND 
# input log-likelihood values 
fmutsel_pan_alt_likelihood <- -10464.152130 
fmutsel_pan_statistic <- 2 * (fmutsel_pan_alt_likelihood - fmutsel_null_likelihood)
p_value4 <- 1 - pchisq(fmutsel_pan_statistic, freedom) # calculate p-value

# create data frame with results
resultsdf4 <- data.frame(name = "fmutsel_pan_alt_TAS1R1", likelihood_ratio_test = fmutsel_pan_statistic, p_value = p_value4)
resultsdf <- rbind(resultsdf, resultsdf4)

```


# TAS1R3 
## Log Likelihood Values (F1x4)
TAS1R3 (Human Foreground): -13255.793870 (parameters = 40)
TAS1R3 (Null): -13256.353434 (parameters = 39)
TAS1R3 (Homo-Pan Foreground): -13252.482815 (parameters = 40)

```{r}
# null likelihood 
f1x4_null_likelihood_r3 <- -13256.353434 

#####################################################################################################################
# HUMAN FOREGROUND 
# input log-likelihood values 
f1x4_hum_alt_likelihood_r3 <- -13255.793870
f1x4_hum_statistic_r3 <- 2 * (f1x4_hum_alt_likelihood_r3 - f1x4_null_likelihood_r3)
p_value5 <- 1 - pchisq(f1x4_hum_alt_likelihood_r3, freedom) # calculate p-value

# create data frame with results
resultsdf5 <- data.frame(name = "f1x4_hum_alt_TAS1R3", likelihood_ratio_test = f1x4_hum_statistic_r3, p_value = p_value5)
resultsdf <- rbind(resultsdf, resultsdf5)

#####################################################################################################################
# HOMININI FOREGROUND 
# input log-likelihood values 
f1x4_pan_alt_likelihood_r3 <- -13252.482815
f1x4_pan_statistic_r3 <- 2 * (f1x4_pan_alt_likelihood_r3 - f1x4_null_likelihood_r3)
p_value6 <- 1 - pchisq(f1x4_pan_statistic_r3, freedom) # calculate p-value

# create data frame with results
resultsdf6 <- data.frame(name = "f1x4_pan_alt_TAS1R3", likelihood_ratio_test = f1x4_pan_statistic_r3, p_value = p_value6)
resultsdf <- rbind(resultsdf, resultsdf6)

```


## Log Likelihood Values (Fmutsel)
TAS1R3 (Human Foreground): -12477.060482 (parameters = 43)
TAS1R3 (Null): -12477.620564 (parameter = 42)
TAS1R3 (Homo-Pan Foreground): -12473.791511 (parameters = 43)

```{r}
# null likelihood 
fmutsel_null_likelihood_r3 <- -12477.620564 

#####################################################################################################################
# HUMAN FOREGROUND 
# input log-likelihood values 
fmutsel_hum_alt_likelihood_r3 <- -12477.060482
fmutsel_hum_statistic_r3 <- 2 * (fmutsel_hum_alt_likelihood_r3 - fmutsel_null_likelihood_r3)
p_value7 <- 1 - pchisq(fmutsel_hum_statistic_r3, freedom) # calculate p-value

# create data frame with results
resultsdf7 <- data.frame(name = "fmutsel_hum_alt_TAS1R3", likelihood_ratio_test = fmutsel_hum_statistic_r3, p_value = p_value7)
resultsdf <- rbind(resultsdf, resultsdf7)

#####################################################################################################################
# HOMININI FOREGROUND 
# input log-likelihood values 
fmutsel_pan_alt_likelihood_r3 <- -12473.791511
fmutsel_pan_statistic_r3 <- 2 * (fmutsel_pan_alt_likelihood_r3 - fmutsel_null_likelihood_r3)
p_value8 <- 1 - pchisq(fmutsel_pan_statistic_r3, freedom) # calculate p-value

# create data frame with results
resultsdf8 <- data.frame(name = "fmutsel_pan_alt_TAS1R3", likelihood_ratio_test = fmutsel_pan_statistic_r3, p_value = p_value8)
resultsdf <- rbind(resultsdf, resultsdf8)

#####################################################################################################################
write.csv(resultsdf, file = "results.csv", row.names = FALSE)

```











